---
title: "How to maintain the `British Columbia Watershed Characterization` application"
author: ""
date: "2022-02-27"
output: 
   html_document:
      theme: cerulean
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
  
  
# File structure

The repository includes two parts of folders and files.

### Application Crucial  
  
  + **app.R**       Initialized this application.  
  + **bcwatershedchara.Rproj**    [R project file](https://r4ds.had.co.nz/workflow-projects.html).  
  + **data**        Stores the data that will be loaded to the application.  
  + **www**         Stores the dependent images, theme setting and html pages.  
  + **renv**        [renv package](https://rstudio.github.io/renv/articles/renv.html) files. These 2 bring project-local R dependency management to your projects. 
  + **renv.lock**
  + **README.md**   First step instruction about how to start the application in Github repository.
  + **.gitignore**  Github file. Do not need to modify it.
    
### Maintain Use  
    
  + **maintain** An R markdown documentation about how to maintain this application.
  + **data-raw** Raw data downloaded.
  + **html** Many markdown files of the html pages used in the application.
      + **images** Used on the theme application, do not modify.
      + **markdown** R markdown files of all html pages used in this application, and CSS theme file.
          + **www** The dependent images that are needed to render the html pages.

# Update and maintain the data used
## HYDAT station data  
  
Recommended to run every quarter to update the database `Hydat_sqlite3_date`
Check here if there is a newer version https://collaboration.cmc.ec.gc.ca/cmc/hydrometrics/www/  
  
```{r, haydattable, eval=FALSE}
library(tidyhydat)
library(fasstr)

# see if you already has HYDAT database
tidyhydat::download_hydat()# then select 1, download HYDAT SQL database now and save to app path
hy_dir() 

# subset Canada-wide stations to BC stations 

#  stations from package fasstr
stationlistBC <- allstations %>% 
                  filter(PROV_TERR_STATE_LOC=="BC") %>%
                  rename_all(tolower) %>%  
                  select(station_number, station_name, latitude, longitude) 
# stations from package tidyhydat
stationlistBC_th <- hy_stations() %>% 
                    filter(PROV_TERR_STATE_LOC=="BC") %>%
                    rename_all(tolower) %>%  
                    select(station_number, drainage_area_gross)
# get application use table
hydattable <- left_join(stationlistBC, stationlistBC_th, by = 'station_number') %>%
              relocate(drainage_area_gross, .before = latitude)

## do not run
# save(hydattable, file = "data/mapdata_hydat.RDa")   # save the hydattable to `projectFolder/data/mapdata_hydat.RDa` for Application loading
```

## Watershed polygon data
Download [Freshwater Atlas Named Watersheds](https://catalogue.data.gov.bc.ca/dataset/freshwater-atlas-named-watersheds) for the entire BC. Put the downloaded data to `projectFolder/data-raw/FWNMDWTRSH_polygon.shp`.
The code below describes how to prepare the watershed polygon layer used in the application. **Run only if the [Freshwater Atlas Named Watersheds](https://catalogue.data.gov.bc.ca/dataset/freshwater-atlas-named-watersheds) has been changed.**

```{r, polygon, eval=FALSE}
# Do not run

# library(sp)
# library(raster)
# library(units)
# library(terra)
# library(sf)
# library(tidyverse)
# 
# FWNMDWTRSH_polygon <- st_transform(read_sf("data-raw/FWNMDWTRSH_polygon.shp", stringsAsFactors = FALSE), crs = 4326)
# Strmrdr_4 <- FWNMDWTRSH_polygon %>% filter(STRMRDR == 4)
# Strmrdr_4$GNIS_ID <- as.character(Strmrdr_4$GNIS_ID)
# Strmrdr4df <- Strmrdr_4 %>% 
#               st_drop_geometry() %>%
#               select(-c(NMDWTRSHDD, BLLNK, FWWTRSHDCD, OBJECTID, FEAT_LEN)) %>%
#               as.data.frame()
# 
# save(Strmrdr_4, Strmrdr4df, file = "data/mapdata_watershed.RDa")
```
  
# Modify and maintain the html pages
  
  This application embodied several html pages:  
  
  + The second page `Watershed Data List` embodied 11 html pages.
  + The third page `User Guide` embodied 1 html pages.
  
  These 12 html pages are generated from 12 R markdown files, which are all located in the `projectFolder/html/markdown/pageNmae.rmd`. To modify the content in these pages, please find the accordingly `/pageName.rmd` file, then modify it (do not modify its [YAML](https://monashdatafluency.github.io/r-rep-res/yaml-header.html) header). After `Knit` the modified `.rmd` file to an html file, manually move this html file to `projectFolder/www/keepSamePageName.html` so the application will call it then loaded.
  
  
  
  *The End*
  

